
%% example document for statsTeachR beamer slides 


%	This path assumes the preamble is in the parent directory,
%		modify this if that changes.
\input{../statsTeachR_preamble_slides}

%	The following variables are assumed by the standard preamble:
%	Global variable containing module name:
\title{Sample Module name}

%        Global variable containing text of authorship acknowledgments and license terms:
\newcommand{\LicenseText}{These slides were adapted for \href{http://statsteachr.org}{statsTeachR} by Nicholas Reich from slides written by Jeff Goldsmith and are released under a \href{http://creativecommons.org/licenses/by-sa/3.0/deed.en_US}{Creative Commons Attribution-ShareAlike 3.0 Unported License}. }



%	******	Document body begins here	**********************

\begin{document}

%	Title page
\begin{frame}[plain]
	\titlepage
\end{frame}

%	******	Everything through the above line must be placed at
%		the top of any TeX file using the statsTeachR standard
%		beamer preamble. 





\begin{frame}{Overview}

	\begin{block}{Diagnostic Test}
		Tool for deciding on something you want to know --- the true status of some outcome --- based on something you can measure.

		\begin{itemize}

			\item{Deciding whether someone has tuberculosis (the outcome) based on the presence or size of a raised swelling (the test) following tuberculin injection.}

			\item{Deciding whether an infant has phenylketonuria (the outcome) based on the blood level of phenylalanine (the test).}

			\item{Deciding whether an infant has phenylketonuria (the outcome) based on the odor of the urine (same outcome of interest, different test).}
		\end{itemize}

	\end{block}

\end{frame}



\begin{frame}{The Gold Standard}

In evaluating a test, must compare results to some ``truth''.

This is provided by the best possible test --- the \emph{gold standard} or \emph{criterion standard} test.

\medskip

	\begin{block}{Why Not Use the Gold Standard?}

		 May be expensive, invasive, or impractical.

		\begin{itemize}

			\item{Gold-standard test for pancreatic cancer involves biopsy of the pancreas;}
			\item{Gold-standard test for Alzheimer's disease is post-mortem brain autopsy.}

		\end{itemize}

	\end{block}

\end{frame}


\end{document}