%	Use the standard preamble for Beamer slides of all 
%		statsTeachR modules
%		(\input, not \include, as \include can't access 
%		things in higher-level directories since it needs 
%		write permission there, which it doesn't have; and 
%		in some settings the preamble may be in a higher-level
%		directory than the source file.)
%	This path assumes the preamble is in the parent directory,
%		modify this if that changes.
\input{../standard_beamer_preamble}

%	The following variables are assumed by the standard preamble:
%	Global variable containing module name:
\title{Module Name}
%	Global variable containing module shortname:
%		(Currently unused, may be used in future.)
\newcommand{\ModuleShortname}{shortName}
%	Global variable containing author name:
\author{Eric A. Cohen}
%	Global variable containing text of license terms:
\newcommand{\LicenseText}{Made available under the Creative Commons Attribution-ShareAlike 3.0 Unported License: http://creativecommons.org/licenses/by-sa/3.0/deed.en\textunderscore US }
%	Instructor: optional, can leave blank.
%		Recommended format: {Instructor: Jane Doe}
\newcommand{\Instructor}{}
%	Course: optional, can leave blank.
%		Recommended format: {Course: Biostatistics 101}
\newcommand{\Course}{}



%	******	Document body begins here	**********************

\begin{document}

%	Title page
\begin{frame}[plain]
	\titlepage
\end{frame}

%	******	Everything through the above line must be placed at
%		the top of any TeX file using the statsTeachR standard
%		beamer preamble. 





\begin{frame}{Overview}

	\begin{block}{Diagnostic Test}
		Tool for deciding on something you want to know --- the true status of some outcome --- based on something you can measure.

		\begin{itemize}

			\item{Deciding whether someone has tuberculosis (the outcome) based on the presence or size of a raised swelling (the test) following tuberculin injection.}

			\item{Deciding whether an infant has phenylketonuria (the outcome) based on the blood level of phenylalanine (the test).}

			\item{Deciding whether an infant has phenylketonuria (the outcome) based on the odor of the urine (same outcome of interest, different test).}
		\end{itemize}

	\end{block}

\end{frame}



\begin{frame}{The Gold Standard}

In evaluating a test, must compare results to some ``truth''.

This is provided by the best possible test --- the \emph{gold standard} or \emph{criterion standard} test.

\medskip

	\begin{block}{Why Not Use the Gold Standard?}

		 May be expensive, invasive, or impractical.

		\begin{itemize}

			\item{Gold-standard test for pancreatic cancer involves biopsy of the pancreas;}
			\item{Gold-standard test for Alzheimer's disease is post-mortem brain autopsy.}

		\end{itemize}

	\end{block}

\end{frame}



\begin{frame}{Sensitivity and Specificity}

\taburulecolor{MainColorMedium}
\tabulinesep=1.5ex
\begin{tabu} to 1.0\textwidth[r]{X[,L,]X[,L,]}
	\rowcolor{MainColorLight}\strong{Sensitivity}                                                                    	&
	\strong{Specificity}
\\
	How good is this test at \textit{detecting cases} of this condition?
	&
	How good is this test at giving a \textit{clean bill of health} to those \textit{without} the condition?
\\\hline
	What proportion, of those with the condition, test positive for the condition?
	&
	What proportion, of those without the condition, test negative for the condition?
\\\hline
	\vspace{-3ex}\begin{displaymath}\frac{true\ positives}{positives\ in\ population}\end{displaymath}\vspace{-3ex}
	&
	\vspace{-3ex}\begin{displaymath}\frac{true\ negatives}{negatives\ in\ population}\end{displaymath}\vspace{-3ex}
\\\hline
	\begin{math}
		Pr(T^{+} \mid D^{+})
	\end{math}
	\newline
	$T^{+}$ --- positive test;\newline
	$D^{+}$ --- disease
	&
	\begin{math}
		Pr(T^{-} \mid D^{-})
	\end{math}
	\newline
	$T^{-}$ --- negative test;\newline
	$D^{+}$ --- no disease
\\
\end{tabu}

\end{frame}


\end{document}