Global F tests and Family-Wise Error Rates
========================================================
### Code for Biostatistics Methods 2, UMass-Amherst, Spring 2014
### by [Nicholas Reich](http://nickreich.github.io)

If you have a lot of predictor variables, you should consider using global F tests. Here is a toy example that shows why. 

We start by picking a number of observations and the number of parameters in our model, $p$. We then generate $p-1$ independent covariates, plus a column of 1s for the design matrix.
```{r}
nObs <- 1000
p <- 100
x <- matrix(rnorm(nObs*p), nrow=nObs)
x <- data.frame(1, x)
colNames <- paste0("x", 1:p)
colnames(x) <- colNames
```

Now we will generate our $y$s completely independently of all of our covariates. None of our $x$ variables are associated with our outcome!
```{r}
y <- rnorm(nObs)
```

But if we fit a linear model that assumes that there ARE relationships bewteen our outcome and all of our $x$ variables, do we see any individually significant $\betas$? If so, how many are significant and are these indiciative of real associations?
```{r}
fmla <- formula(paste0("y ~ 0 +", paste(colNames, collapse="+")))
mlr1 <- lm(fmla, data=x)
coefs <- summary(mlr1)$coef
sum(coefs[,"Pr(>|t|)"]<.05)
```

Alternatively, we could use a Global $F$-test to test whether any of the $x$ variables add significant explanatory power to our model. What conclusion do we draw from this test?
```{r}
mlr0 <- lm(y ~ x1, data=x)
anova(mlr0, mlr1)
```

Do the results from the Global $F$-test and the individual $\beta$ $t$-tests agree? Why?

