An example R Markdown file with Mother/Daughter heights data
========================================================
### Biostatistics in Practice HPC workshop, February 2014

```{r loadData, message=FALSE}
require(alr3)
data(heights)
```
The heights dataset contains `r nrow(heights)` observations of heights of a mother and her daughter. This dataset was compiled by the statistician Karl Pearson in the late 1800s. To make this a more interesting example of a permutation test, we will limit our sample size and only consider a random sample of 200 rows of the dataset. We will start by describing the data visually with a simple graphic.

```{r}
summary(heights)
```

Now let's plot the data using ggplot2.  First we're going to plot side by side boxplots of the mother's heights next to the daughter's heights.  

```{r}
require(ggplot2)
heightStack <- data.frame(height = c(heights$Mheight,heights$Dheight),who = factor(c(rep("Mother",1375),rep("Daughter",1375)),levels=c("Mother","Daughter")))
ggplot(heightStack,aes(who,height)) + geom_boxplot(outlier.colour="darkgreen",aes(fill=who)) 
```

Now we'll do a scatter plot of mother's heights versus daughter's heights. The first line in the code below changes the theme.  qplot acts similarly to base R command plot.  

```{r, message=FALSE, fig.height=4, fig.width=5}
theme_set(theme_bw()) ## sets default white background theme for ggplot
qplot(Mheight, Dheight, data=heights, col="red", alpha=.5) + theme(legend.position="none") 
```

We can also do this using ggplot.  

```{r describeData, message=FALSE, fig.height=4, fig.width=5}
theme_set(theme_bw()) ## sets default white background theme for ggplot
ggplot(heights,aes(Mheight, Dheight)) + geom_point(col="red",alpha=0.5) + stat_smooth()
```

